From Reversible Programs to \\ Univalent Universes and Back

### 2021-06-23 Pi+/paper/reversible1.tex
map

As explained in the previous section, a $\Pi$-type $A$ has $\sizet{A}$-elements and for all combinators $c : A \iso B$
we have that $\sizet{A} = \sizet{B}$. Hence the denotation of a type $A$ with $n$-elements will be a finite set
$\Fin[n]$ and the denotation of a combinator $c : A \iso B$ such that $\sizet{A} = \sizet{B} = n$ will be a function
from $\Fin[n]$ to $\Fin[n]$ that permutes the elements. In more detail, we enumerate the values $v : A$ where
$\sizet{A} = n$ in a canonical order such that each value $v$ is given an index in $\{ 0,\cdots,n-1 \}$. The enumeration
is defined as follows:
\[\begin{array}{rcl}
    \mathit{enum}(\zerot) &=& \emptyset \\
    \mathit{enum}(\onet) &=& \{ \Acon{tt} \} \\
    \mathit{enum}(A + B) &=& \mathit{map}~\Acon{inj₁}~\mathit{enum}(A) ~\textsf{+\!+}~ \mathit{map}~\Acon{inj₂}~\mathit{enum}(B) \\
    \mathit{enum}(A \times B) &=& \mathit{concat}~(\mathit{map}~(\lambda w.\mathit{map}~(\lambda v. (v,w))~\mathit{enum}(A))~\mathit{enum}(B))
\end{array}\]
\noindent For example, the 3 values $\inlv{\Acon{tt}}$, $\inrv{(\inlv{\Acon{tt}})}$, and $\inrv{(\inrv{\Acon{tt}})}$ of
type $\onet + (\onet + \onet)$ are given indices 0, 1, and 2 respectively. Given this canonical order, the combinator
$\swapp : \onet + (\onet + \onet) \iso (\onet + \onet) + \onet$ would correspond to the permutation $(1~2~0)$ while the
combinator $\assoclp : \onet + (\onet + \onet) \iso (\onet + \onet) + \onet$ at the same type would correspond to the
identity permutation.

>>>>

As explained in the previous section, a $\Pi$-type $A$ has $\sizet{A}$-elements and for all combinators $c : A \iso B$
we have that $\sizet{A} = \sizet{B}$. Hence the denotation of a type $A$ with $n$-elements will be a finite set
$\Fin[n]$ and the denotation of a combinator $c : A \iso B$ such that $\sizet{A} = \sizet{B} = n$ will be a function
from $\Fin[n]$ to $\Fin[n]$ that permutes the elements. In more detail, we enumerate the values $v : A$ where
$\sizet{A} = n$ in a canonical order such that each value $v$ is given an index in $\{ 0,\cdots,n-1 \}$. The enumeration
is defined as follows:
\[\begin{array}{rcl}
    \mathit{enum}(\zerot) &=& \emptyset \\
    \mathit{enum}(\onet) &=& \{ \Acon{tt} \} \\
    \mathit{enum}(A + B) &=& \mathit{map}~\Acon{inj₂}~\mathit{enum}(A) ~\textsf{+\!+}~ \mathit{map}~\Acon{inj₁}~\mathit{enum}(B) \\
    \mathit{enum}(A \times B) &=& \mathit{concat}~(\mathit{map}~(\lambda v.\mathit{map}~(\lambda w. (v,w))~\mathit{enum}(B))~\mathit{enum}(A))
\end{array}\]
\noindent For example, the 3 values $\inrv{(\inrv{\Acon{tt}})}$, $\inrv{(\inlv{\Acon{tt}})}$, and $\inlv{\Acon{tt}}$ of
type $\onet + (\onet + \onet)$ are given indices 0, 1, and 2 respectively. Given this canonical order, the combinator
$\swapp : \onet + (\onet + \onet) \iso (\onet + \onet) + \onet$ would correspond to the permutation $(1~2~0)$ while the
combinator $\assoclp : \onet + (\onet + \onet) \iso (\onet + \onet) + \onet$ at the same type would correspond to the
identity permutation.
